Anomalous waves triggered by abrupt depth changes: laboratory experiments and truncated KdV statistical mechanics

### 2020-01-03 paper2_JNLS/paper.tex
NNM

% PACKAGES
\usepackage{graphicx, amsmath, amssymb, amsfonts, mathtools, mathrsfs, color}
\usepackage{comment, enumerate, tabularx, todonotes}
\usepackage{natbib, hyperref, url}
\usepackage[margin=1in]{geometry}
%\usepackage[justification=RaggedRight]{caption}

@@

\author{
M.~N.~J.~Moore\thanks{Florida State University}, 
C.~Tyler Bolles\thanks{University of Michigan},
Andrew J.~Majda\thanks{Courant Institute of Mathematical Sciences}, 
Di Q\footnotemark[3] }
\maketitle

@@

Rogue waves are abnormally large surface waves, defined by oceanographers as those that exceed twice the significant wave height \citep{muller2005rogue, ying2011linear}. Though such waves were once dismissed as myth, they have now been recorded in oceans across the globe and pose a recognized threat to seagoing vessels and naval structures. Rogue waves, also variously known as freak or anomalous waves, have been observed in shallow \cite{pelinovsky2000nonlinear, gramstad2013freak}, intermediate \cite{karmpadakis2019laboratory}, and deep water \cite{dematteis2018rogue, dematteis2019experimental}, and certain rogue features have even been recovered by exact solutions to various wave models \cite{peregrine1983water, clarkson2017rational, chen2019periodic}.
These abnormal waves can be triggered by a variety of mechanisms, including anomalous wind-forcing \citep{kharif2008influence, toffoli2017wind}, opposing currents \citep{garrett2009rogue, onorato2011triggering}, focusing due to variable bathymetry \citep{heller2008refraction, white1998chance}, 
and the Benjamin-Feir deep-water modulational instability \citep{benjamin1967disintegration, viotti2013emergence, cousins2015unsteady, farazmand2017reduced}.
The common tie between these mechanisms is their ability to generate non-normal statistics in the surface displacement: when governed by Gaussian statistics, the likelihood of a rogue wave is extremely low, but these events occur much more frequently when surface statistics deviate from Gaussian. In this way, anomalous waves can be approached from the broader perspective of turbulent dynamical systems \cite{sapsis2013a, sapsis2013b, sapsis2013blending, chen2016filtering, majda2016introduction, macedo2017universality, MajdaQiSIAM2018, blonigan2019extreme, guth2019machine, holm2019stochastic}.

>>>>

% PACKAGES
\usepackage{graphicx, amsmath, amssymb, amsfonts, mathtools, mathrsfs, color}
\usepackage{comment, enumerate, tabularx, todonotes}
\usepackage{hyperref, url}
\usepackage[margin=1in]{geometry}
%\usepackage[justification=RaggedRight]{caption}

@@

\author{
M.~N.~J.~Moore\thanks{Florida State University}, 
C.~Tyler Bolles\thanks{University of Michigan},
Andrew J.~Majda\thanks{Courant Institute of Mathematical Sciences}, 
Di Qi\footnotemark[3] }
\maketitle

@@

Rogue waves are abnormally large surface waves, defined by oceanographers as those that exceed twice the significant wave height \cite{muller2005rogue, ying2011linear}. Though such waves were once dismissed as myth, they have now been recorded in oceans across the globe and pose a recognized threat to seagoing vessels and naval structures. Rogue waves, also variously known as freak or anomalous waves, have been observed in shallow \cite{pelinovsky2000nonlinear, gramstad2013freak}, intermediate \cite{karmpadakis2019laboratory}, and deep water \cite{dematteis2018rogue, dematteis2019experimental}, and certain rogue features have even been recovered by exact solutions to various wave models \cite{peregrine1983water, clarkson2017rational, chen2019periodic}.
These abnormal waves can be triggered by a variety of mechanisms, including anomalous wind-forcing \cite{kharif2008influence, toffoli2017wind}, opposing currents \cite{garrett2009rogue, onorato2011triggering}, focusing due to variable bathymetry \cite{heller2008refraction, white1998chance}, 
and the Benjamin-Feir deep-water modulational instability \cite{benjamin1967disintegration, viotti2013emergence, cousins2015unsteady, farazmand2017reduced}.
The common tie between these mechanisms is their ability to generate non-normal statistics in the surface displacement: when governed by Gaussian statistics, the likelihood of a rogue wave is extremely low, but these events occur much more frequently when surface statistics deviate from Gaussian. In this way, anomalous waves can be approached from the broader perspective of turbulent dynamical systems \cite{sapsis2013a, sapsis2013b, sapsis2013blending, chen2016filtering, majda2016introduction, macedo2017universality, MajdaQiSIAM2018, blonigan2019extreme, guth2019machine, holm2019stochastic}.
